What covert verbal actions tell us about the interplay between language, action, and perception

### 2021-04-09 manuscript.tex
minor updates to readme file

How does motor learning/experience influence the multisensory content/experience of motor imagery and covert verbal actions? In other words, how to the motor and perceptual system interact during covert verbal actions? In the first subsection, we discuss two mechanisms that may be responsible for providing the sensory content of covert verbal actions and their respective involvement and delimitations. In the second subsection, we discuss an exciting avenue for investigating the influence of motor learning on the sensory content of imagined actions, namely studying the imagery ot totally novel (i.e., never executed) actions...

@@

The balance between these two mechanisms may depend by the precise instructions given to the participants (cf. Fig \ref{fig:1}). More precisely, depending on whether they are instructed to "imagine speaking" or "imagine hearing" speech (similar to the distinction between the "inner ear" and the "inner voice", e.g., \cite{smith_subvocalization_1992})... distinct MEG correlates and effects on a subsequent categorisation task \citep{ma_distinct_2019}...

In the absence of non-ambiguous instructions, the balance between these two mechanisms may depend on situational (e.g., surrounding noise) and intrinsic (e.g., expertise), in brief on computational cost/resource, concept of memoisation \citep{dasgupta_memory_2021}... In other words, situational (extrinsic) and individual (intrinsic) characteristics jointly determine the computational cost (or equivalently, the available computational resources), which in turn determines the balance between the simulation and association mechanisms. Novel and/or difficult tasks may rely more on the simulation mechanism whereas well known tasks may rely more on associative mechanisms... See also the discussion in  \citep{nalborczyk_understanding_2019-1, nalborczyk_re-analysing_2020}...

@@

One obvious difference subsist between overt and covert verbal actions, namely that covert actions are not accompanied by overt movements... This puzzle, coined as \textit{the problem of inhibition} by \cite{jeannerod_neural_2001}, can be summarised as follows: given the putative role of the motor system in providing the multisensory perceptual content of motor imagery, how is it possible for motor imagery not to lead to motor execution?

@@

Neural correlates... the inhibitory triangle (cf. Fig \ref{fig:2}), composed of the preSMA, the rIFC, and the STN... A functional dissociation between the preSMA and the rIFC \citep{diesburg_pause-then-cancel_2021}... Moreover, they also reported a reduced short-interval intracortical inhibition (SICI) in patients with TS, a phenomenon that has been shown to be involved in response inhibition during motor imagery \citep{neige_unravelling_2020}...

@@

\cite{watson_psychology_1919} first suggested that thought (inner speech, in the terminology) was rooted in (overt) speech, that is, that it matured from overt speech... Vygotsky idea of speech internalisation and development of inhibition... Vygotsky observed, as Piaget did before, that egocentric or "private" speech tend to be internalised during child development... \cite{fernyhough_alien_2004} extended this model... What if speech internalisation was related to the development of inhibitory abilities?

These ideas could be assessed experimentally in several ways. First, the relation between speech internalisation and inhibitory abilities could be assessed during development at the critical ages (i.e., between 6 and 8 years). We would expect the ability to imagine actions and speech specifically to be positively correlated with inhibitory skills at at this stage. Second, the inhibitory perspective presented here could be causally assessed by manipulation the inhibitory network preventing execution during motor imagery. For instance, using TMS... \citep{angelini_motor_2015, angelini_proactive_2016}... Third and finally, inhibition "deficits" in Tourette syndrom...

>>>>

How does motor learning/experience influence the multisensory content/experience of motor imagery and covert verbal actions? In other words, how to the motor and perceptual system interact during covert verbal actions? In the first subsection, we discuss two mechanisms that may be responsible for providing the sensory content of covert verbal actions and their respective involvement and delimitation. In the second subsection, we discuss an exciting avenue for investigating the influence of motor learning on the sensory content of imagined actions, namely studying the imagery ot totally novel (i.e., never executed) actions...

@@

The balance between these two mechanisms may depend by the precise instructions given to the participants (see Figure \ref{fig:1} for a summary). More precisely, depending on whether they are instructed to "imagine speaking" or "imagine hearing" speech (similar to the distinction between the "inner ear" and the "inner voice", e.g., \cite{smith_subvocalization_1992})... distinct MEG correlates and effects on a subsequent categorisation task \citep{ma_distinct_2019}...

In the absence of non-ambiguous instructions, and in line with \cite{tian_mental_2012}, we suggest that the balance between these two mechanisms may depend on situational (e.g., surrounding noise) and intrinsic (e.g., expertise) characteristics. In addition to \cite{tian_mental_2012}, we suggest that a common currency determining the use of one of these mechanisms is the computational cost/resource, concept of memoisation \citep{dasgupta_memory_2021}... In other words, situational (extrinsic) and individual (intrinsic) characteristics jointly determine the computational cost (or equivalently, the available computational resources), which in turn determines the balance between the simulation and association mechanisms. Novel and/or difficult tasks may rely more on the simulation mechanism whereas well known tasks may rely more on associative mechanisms... See also the discussion in  \citep{nalborczyk_understanding_2019-1, nalborczyk_re-analysing_2020}...

@@

One obvious difference subsist between overt and covert verbal actions, namely that covert actions are not accompanied by overt movements... This puzzle, coined as \textit{the problem of inhibition} by \cite{jeannerod_neural_2001}, can be summarised as follows: given the putative role of the motor system in providing the multisensory perceptual content of motor imagery, how is it possible for motor imagery not to lead to motor execution? We outline some working hypotheses regarding these mechanisms and their plausible roles in certain inhibitory disorders...

@@

Neural correlates... the inhibitory triangle (cf. Figure \ref{fig:2}), composed of the preSMA, the rIFC, and the STN... A functional dissociation between the preSMA and the rIFC \citep{diesburg_pause-then-cancel_2021}... Moreover, they also reported a reduced short-interval intracortical inhibition (SICI) in patients with TS, a phenomenon that has been shown to be involved in response inhibition during motor imagery \citep{neige_unravelling_2020}...

@@

\cite{watson_psychology_1919} suggested that thought (i.e., covert speech, in his terminology) was rooted in (overt) speech, that is, that it matured from overt speech... Vygotsky idea of speech internalisation and development of inhibition... Vygotsky observed, as Piaget did before, that egocentric or "private" speech tend to be internalised during child development... \cite{fernyhough_alien_2004} extended this model... What if speech internalisation was related to the development of inhibitory abilities?

These ideas could be assessed experimentally in several ways. First, the relation between speech internalisation and inhibitory abilities could be assessed during development at the critical ages (i.e., between 6 and 8 years). We would expect the ability to imagine actions and speech specifically to be positively correlated with inhibitory skills at at this stage. Second, the inhibitory perspective presented here could be causally assessed by manipulation the inhibitory network preventing execution during motor imagery. For instance, using TMS, can we brake these inhibitory mechanisms and "force" execution during motor imagery... \citep{angelini_motor_2015, angelini_proactive_2016}... Third and finally, inhibition "deficits" in Tourette syndrom...
